Supplementary material for ``Screening Sinkhorn Algorithm for regularized Optimal Transport''

### 2019-05-21 tex/v3/section_1_introduction.tex
intro

	\item From a methodological point of view, we propose a reformulation the dual of the Sinkhorn divergence problem by imposing variables to be larger than a threshold.
	This formulation allows us to introduce sufficient conditions, computable beforehand, for a variable to be strictly satisfied its constraint, leading then to
	a ``screened'' version of the dual of Sinkhorn divergence. 
	\item We provide some theoretical analysis of the solution of the ``screened''  Sinkhorn divergence, showing that its objective value and the marginal constraint satisfaction are properly controlled 	as the number of screened variables decreases.
	\item From an algorithmic standpoint, we use a constrained LBFGS algorithm \cite{nocedal1980,byrd1995L-BFGS-B} but provide a careful analysis of the lower bound and upper bound of the dual	variables, resulting in a well-posed and efficient algorithm denoted as \emph{Screenkhorn}.
	\item Our empirical analysis depicts how the approach behaves in a simple Sinkhorn divergence computation context. When considered in  complex machine learning
	pipelines, we show that \emph{Screenkhorn} can lead to strong gain in efficiency
	while not compromising on accuracy.
\end{itemize}}
%	
%
%These constraints are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
%We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
%Furthermore, the active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
%We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
%Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained box-constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,byrd1995L-BFGS-B} that relies on an estimation of the inverse of the Hessian based on gradients differences. 
%L-BFGS-B algorithm was adapted to the OT setting via the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.}

>>>>

	\item From a methodological point of view, we propose a reformulation the dual of the Sinkhorn divergence problem by imposing variables to be larger than a threshold.
	This formulation allows us to introduce sufficient conditions, computable beforehand, for a variable to be strictly satisfied its constraint, leading then to
	a ``screened'' version of the dual of Sinkhorn divergence. 
	\item We provide some theoretical analysis of the solution of the ``screened''  Sinkhorn divergence, showing that its objective value and the marginal constraint satisfaction are properly controlled 	as the number of screened variables decreases.
	\item From an algorithmic standpoint, we use a constrained LBFGS algorithm \citep{nocedal1980,byrd1995L-BFGS-B} but provide a careful analysis of the lower bound and upper bound of the dual	variables, resulting in a well-posed and efficient algorithm denoted as \emph{Screenkhorn}.
	\item Our empirical analysis depicts how the approach behaves in a simple Sinkhorn divergence computation context. When considered in  complex machine learning
	pipelines, we show that \emph{Screenkhorn} can lead to strong gain in efficiency
	while not compromising on accuracy.
\end{itemize}}
%	
%
%These constraints are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
%We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
%Furthermore, the active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
%We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
%Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained box-constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,byrd1995L-BFGS-B} that relies on an estimation of the inverse of the Hessian based on gradients differences. 
%L-BFGS-B algorithm was adapted to the OT setting via the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.}
